Article results

### 2022-06-19 analysis/article-results.Rmd
Definitively stick with lambda min, 1se too poor

# Source functions
source("data-raw/prepare_raw_data.R")
source("R/imputation-helpers.R")
source("R/model-validation-helpers.R")

@@

```{r objs}
tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin
  )
)

@@

```{r dev-calib}
X_dev <- subset(x = stats::model.matrix(model_formula, data = imps_develop), select = -`(Intercept)`)
y_dev <- imps_develop[[response_var]]
lp_dev <- drop(predict(mod_develop, newx = X_dev, type = "link")) # linear predictor

# Make df for calibration
df_calplot_develop <- cbind.data.frame(lp_dev, imps_develop)

# We use restricted cubic splines with 4 knots
knots <- 4

# Get limits of predicted probabilities across all imputed datasets
pred_probs <- plogis(df_calplot_develop$lp_dev) 
probs_grid <- seq(min(pred_probs), max(pred_probs), by = 0.005)
lp_grid <- qlogis(probs_grid)

# The "average" smooth calibration is simply the one fitted on stacked data
mod_cal_stacked <- glm(
  formula = Mc_FailedFemoralApproach ~ ns(lp_dev, knots), 
  data = df_calplot_develop, 
  family = binomial()
)

# No easy way to create CI for this, so we visualise all the calibration curves
# in each imputed dataset:
split(df_calplot_develop, ~ .imp) %>%
  map(
    .f = ~ {
      mod_cal <- glm(
        formula = Mc_FailedFemoralApproach ~ ns(lp_dev, knots), 
        data = .x, 
        family = binomial()
      )
      data.frame(
        "predicted" = probs_grid,
        "observed" = predict(mod_cal, newdata = data.frame("lp_dev" = lp_grid), type = "response"),
        row.names = NULL
      )
    }
  ) %>%
  bind_rows(.id = ".imp") %>%
  ggplot() +
  geom_line(aes(group = .imp, x = predicted, y = observed), alpha = 0.8, col = "lightgray", size = 1) +
  theme(panel.grid.major = element_blank()) + 
  geom_line(
    data = cbind.data.frame(
      "predicted" = probs_grid,
      "observed" = predict(
        mod_cal_stacked, 
        newdata = data.frame("lp_dev" = lp_grid), 
        type = "response"
      ) #- 0.25
    ),
    aes(x = predicted, y = observed),
    size = 2
  ) +
  geom_abline(intercept = 0, slope = 1, col = "red", size = 1, linetype = "dashed") #+
  geom_histogram(
    data = df_calplot_develop, 
    aes(x = plogis(lp_dev), 
        y = stat(
          0.25 * count / max(count)
        )#0.5 * (..count../sum(..count..))
      ),
    fill = "lightblue",
    bins = 100
  )

# Work this later..

# Add hists of pred probs/annotation of AUC, slope and int?
df_calplot_develop |> 
  ggplot(aes(plogis(lp_dev))) +
  geom_histogram()
```

@@

X_valid <- subset(x = stats::model.matrix(model_formula, data = imps_valid), select = -`(Intercept)`)
y_valid <- imps_valid[[response_var]]

@@

#
pred_probs <- plogis(df_calplot_valid$lp_valid)
probs_grid <- seq(min(pred_probs), max(pred_probs), by = 0.01)
lp_grid <- qlogis(probs_grid)

mod_cal_stacked_valid <- glm(
  formula = Mc_FailedFemoralApproach ~ ns(lp_valid, knots), 
  data = df_calplot_valid, 
  family = binomial()
)

# Now calplot
split(df_calplot_valid, ~ .imp) %>%
  map(
    .f = ~ {
      mod_cal <- glm(
        formula = Mc_FailedFemoralApproach ~ ns(lp_valid, knots), 
        data = .x, 
        family = binomial()
      )
      data.frame(
        "predicted" = probs_grid,
        "observed" = predict(mod_cal, newdata = data.frame("lp_valid" = lp_grid), type = "response"),
        row.names = NULL
      )
    }
  ) %>%
  bind_rows(.id = ".imp") %>%
  ggplot() +
  geom_line(aes(group = .imp, x = predicted, y = observed), alpha = 0.8, col = "lightgray", size = 1) +
  theme(panel.grid.major = element_blank()) + 
  geom_line(
    data = cbind.data.frame(
      "predicted" = probs_grid,
      "observed" = predict(
        mod_cal_stacked_valid, 
        newdata = data.frame("lp_valid" = lp_grid), 
        type = "response"
      )
    ),
    aes(x = predicted, y = observed),
    size = 2
  ) +
  geom_abline(intercept = 0, slope = 1, col = "red", size = 1, linetype = "dashed") +
  lims(x = c(0, 0.8), y = c(0, 0.8))
```

@@

```{r combined-validation}

```

>>>>

# Source functions
source("data-raw/prepare_raw_data.R")
source("R/imputation-helpers.R")
source("R/model-validation-helpers.R")
source("R/calplot-MI.R")

@@

```{r objs}
tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin,
    validation_comb_lambdamin
  )
)

@@

```{r dev-calib}
calplot_MI(
  imps_long = imps_all %>% 
    filter(imps_label == "imps_assess" & dataset == "develop"),
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 100,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

@@

X_valid <- subset(x = stats::model.matrix(model_formula, data = imps_valid), select = -`(Intercept)`)

@@

calplot_MI(
  imps_long = imps_valid,
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

Try intermediate updating with logreg recalibration

```{r updating}
mod_coefs
log_recal <- glm(imps_valid$Mc_FailedFemoralApproach ~ lp_valid, family = binomial())
coef(log_recal)

news_coefs <- c(coef(log_recal)[[1]], coef(log_recal)[[2]] * drop(mod_coefs)[-1])
new_lp <- drop((news_coefs) %*% t(cbind(1, X_valid)))

df_calplot <- cbind.data.frame("lp" = new_lp, imps_valid)
knots <- 4
smooth_form <- reformulate(response = response_var, termlabels = paste0("splines::ns(lp, ", knots, ")"))
mod_cal_stacked <- glm(formula = smooth_form, data = df_calplot, family = binomial())
stacked_df <- data.frame(
    "predicted" = unique(plogis(new_lp)),
    "observed" = predict(mod_cal_stacked, 
                         newdata = data.frame("lp" = unique(plogis(new_lp))), 
                         type = "response")
)
plot(stacked_df$predicted, stacked_df$observed)
```

@@

```{r combined-validation}
imps_combined <- imps_all %>% 
  filter(imps_label == "imps_combined")

mod_combined <- validation_comb_lambdamin$model_fit
validation_comb_lambdamin$model_fit$lambda

validation_comb_lambdamin$validation_summary
validation_comb_lambdamin$validation_df |> 
  ggplot(aes(x = corrected)) +
  geom_histogram(bins = 50) +
  facet_wrap(~ measure, scales = "free")

validation_comb_lambdamin$validation_df |> 
  group_by(boot_num) |> 
  summarise(pen = mean(penalty)) |>
  #pull(pen) |>  mean()
  ggplot(aes(pen)) +
  geom_histogram()

calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.5),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal()

# Try the 1se on combined:
imputations <- imps_combined
formula <- model_formula
n_folds = 10
wts <- "wts"
lambda_choice <- "1se"

response_var <- all.vars(stats::update(formula, . ~ 1))
  X_orig <- subset(x = stats::model.matrix(formula, data = imputations), select = -`(Intercept)`)
  y_orig <- imputations[[response_var]]
  wts_orig <- imputations[[wts]]

  # First apparent performance
  folds <- assign_crossval_folds(y = unique(imputations[[".id"]]), n_folds = n_folds)
  mod_orig <- run_lasso_glmnet(
    x = X_orig,
    y = y_orig,
    wts = wts_orig,
    foldid = folds[match(imputations[[".id"]], folds[["y"]]), "fold"],
    lambda_choice = lambda_choice
  )

mod_orig$lambda
calplot_MI(
  imps_long = imps_combined,
  model = mod_orig,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 3,
  n_bins = 200,
  xlim = c(0, 0.5),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal() 
```
